A DPG method for compressible flow problems

### 2012-07-16 docs/Jesse/Proposal/NSNotes.tex

For our solver, we use a standard pseudo-time solver and greedy refinement scheme. Though we have not yet implemented adaptive timestepping, we are able to take large enough uniform timesteps over a coarse mesh such that convergence is order-of-magnitude comparable to the convergence of a damped Newton method.

@@

We take the computational domain to be $\Omega = [0,2]\times[0,1]$. For $\Reyn = 1000$, we experimented with initial meshes from size 4 by 8 to 8 by 16 elements. We note that, on a very coarse initial mesh (4 by 8 elements), the convergence of the pseudo-timestep stagnates at around a transient residual of $1e-6$; however, if we lower the tolerance only for the first step and continued with the adaptive algorithm, the solution converges below $\epsilon_t$ for all refined meshes.

\begin{figure}[!h]
\centering
\subfigure[$\rho$]{\includegraphics[scale=.42]{figs/Re1000p2/rho.pdf}}
\subfigure[$u_1$]{\includegraphics[scale=.42]{figs/Re1000p2/u1.pdf}}
\subfigure[$u_2$]{\includegraphics[scale=.42]{figs/Re1000p2/u2.pdf}}
\subfigure[$T$]{\includegraphics[scale=.42]{figs/Re1000p2/T.pdf}}
\caption{Solutions after six refinements for $p=2$ and $\Reyn = 1000$.}
\label{fig:Re500}
\end{figure}

\begin{figure}[!h]
\centering
\subfigure[$\rho$]{\includegraphics[scale=.4]{figs/Re1000p2/rhozoom.pdf}}
\subfigure[$u_1$]{\includegraphics[scale=.4]{figs/Re1000p2/u1zoom.pdf}}
\subfigure[$u_2$]{\includegraphics[scale=.4]{figs/Re1000p2/u2zoom.pdf}}
\subfigure[$T$]{\includegraphics[scale=.4]{figs/Re1000p2/Tzoom.pdf}}
\caption{Zoom of solutions at the beginning of the plate for $p=2$ and $\Reyn = 1000$.}
\label{fig:Re500}
\end{figure}

%For $p=2$, after six refinements, the energy error is 0.000410347. After refinement, mesh has 1083 elements and 143910 global dofs.

\begin{figure}[!h]
\centering
%\subfigure[$p=2$]{\includegraphics[scale=.5]{figs/Re1000p2/mesh.pdf}}
%\subfigure[$p=3$]{\includegraphics[scale=.5]{figs/Re1000p3/mesh.pdf}}
\includegraphics[scale=.55]{figs/Re1000p2/mesh.pdf}
\caption{Adaptive mesh after six refinements for $p=2$
% and five refinements for $p=3$ 
with $\Reyn = 1000$.}
\label{fig:MeshRe1000}
\end{figure}

>>>>

For our solver, we use a standard pseudo-time solver and greedy refinement scheme. Though we have not yet implemented adaptive timestepping, we are able to take large enough uniform timesteps over a coarse mesh such that convergence occurs sufficiently quickly.

@@

We take the computational domain to be $\Omega = [0,2]\times[0,1]$. We begin with a mesh of 8 by 16 elements. Under Dirichlet wall boundary conditions for all 3 traces $u_1$, $u_2$, and $T$, the solution develops a singularity in the density $\rho$ at the plate beginning, and both $T$ and $u_1$ form a boundary layer along the leading edge of the plate. Due to the presence of the singularity, the solution for $\rho$ is scaled such that the features of the solution away from the singularity are visible in Figure~\ref{fig:rhoScaled}.

\begin{figure}[!h]
\centering
\subfigure[$\rho$]{\includegraphics[scale=.21]{figs/Re1000p2/rhoUnscaled.png}}
\subfigure[$u_1$]{\includegraphics[scale=.21]{figs/Re1000p2/u1.png}}
\subfigure[$u_2$]{\includegraphics[scale=.21]{figs/Re1000p2/u2.png}}
\subfigure[$T$]{\includegraphics[scale=.21]{figs/Re1000p2/T.png}}
\caption{Solutions after seven refinements for $p=2$ and $\Reyn = 1000$.}
\label{fig:Re500}
\end{figure}

\begin{figure}[!h]
\centering
\subfigure[$\rho$]{\includegraphics[scale=.25]{figs/Re1000p2/rhoScaled.png}}
\subfigure[Mesh]{\includegraphics[scale=.57]{figs/Re1000p2/mesh6.png}}
\caption{Rescaled solution for $\rho$ in the range $[0,3]$ and adaptive mesh after seven refinements.}
\label{fig:rhoScaled}
\end{figure}

\begin{figure}[!h]
\centering
\subfigure[$\rho$]{\includegraphics[scale=.23]{figs/Re1000p2/rhoUnscaledzoom.png}}
\subfigure[$u_1$]{\includegraphics[scale=.23]{figs/Re1000p2/u1zoom.png}}
\subfigure[$u_2$]{\includegraphics[scale=.23]{figs/Re1000p2/u2zoom.png}}
\subfigure[$T$]{\includegraphics[scale=.23]{figs/Re1000p2/Tzoom.png}}
\caption{Zoom of solutions at the beginning of the plate for $p=2$ and $\Reyn = 1000$.}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[scale=.45]{figs/Re1000p2/heatflux.png}
\caption{Heat flux at the bottom boundary.}
\end{figure}

### 2012-07-16 docs/Jesse/Proposal/outline.tex
added committee members to outline

\usepackage{utdiss2}  		% Dissertation package style file.

@@

\committeemembers
	[Committee member 1]
	[Committee member 2]
	{Committee member 3}

@@

\begin{document}
\copyrightpage          % Produces the copyright page.
\commcertpage           % Produces the Committee Certification
\titlepage

\begin{dedication}
\index{Dedication@\emph{Dedication}}%
Dedicated to \ldots
\end{dedication}

\begin{acknowledgments}		% Optional
\index{Acknowledgments@\emph{Acknowledgments}}%
I wish to thank the multitudes of people who helped me. Time would
fail me to tell of \ldots
\end{acknowledgments}

\utabstract
\index{Abstract}%
\indent
This document has the form of a ``fake'' doctoral dissertation
in order to provide an example of such, but it is actually a
copy of Miguel Lerma's documentation for the Mathematics
Department Computer Seminar of 25 March 1998 updated in July 2001
and following by Craig McCluskey to meet the March 2001
requirements of the Graduate School.

This document and its source file show to write a Doctoral Dissertation using 
\LaTeX{} and the utdiss2 package.

>>>>

\usepackage{utproposal}  		% Dissertation package style file.

@@

\committeemembers
	[Todd Arbogast]
	[Omar Ghattas]
	{Venkat Raman}

@@

\begin{document}
%\copyrightpage          % Produces the copyright page.
%\commcertpage           % Produces the Committee Certification
\titlepage
